---
title: "(Reproducible) Data Visualisation with R and how to make interactive things with R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repo contains my 2022-07-13 talk for the [Artificial Intelligence for Scientific Discovery Network+ (AI3SD)](https://www.ai4science.network/ai3sd-event/13-14-07-2022-failed-it-to-nailed-it-nailing-your-data-visualisation-hands-on-workshop/) workshop *Nailing your Data Visualisation: Training Workshop*.

Please note that this talk is approximately 50% live coding so the slides won't make too much sense on their own. [You can download the code I wrote during the workshop](https://drive.google.com/file/d/1QbZR2Bca2MYdbynKCebq85LTblXAKv2W/view?usp=sharing).

During the talk I made use of this etherpad, [pad.riseup.net/p/2022-07-13_cjh](https://pad.riseup.net/p/2022-07-13_cjh). I've stored the contents of the etherpad in the `talk-etherpad.md` file.

## Required packages

To follow along with the live coding you will need to install several packages:

```{r, eval=FALSE}
install.packages(c("fivethirtyeight", "fontawesome", "ggplot2", 
  "here", "highcharter", "janitor", "leaflet", "plotly", "rmarkdown", "rnaturalearthdata", 
  "sf", "shiny", "tidyverse", "xaringan", "visNetwork"))
```

